### 2020-09-11 sections/working-papers.tex
Update working-papers.tex

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. ({\itshape forthcoming}).  Applying ForceAtlas2, a Continuous Graph LayoutAlgorithm, to the Elites Study. Tufte Working Papers, (1), 1--13. {\footnotesize \scshape [in Spanish]}.} \vspace{1mm}

@@

\end{cventries}

>>>>

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. (2020).  Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study. {\itshape Tufte Working Papers}, (1), 1--15. {\footnotesize \scshape [in Spanish]}. {\scshape url:} \href{https://tuftepapers.com/2020/09/aplicacion-de-ForceAtlas2-algoritmo-de-diseno-grafico.html}{\textcolor{blue}{https://tuftepapers.com}}. {\scshape {\footnotesize SocArXiv} doi:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}

@@

\end{publications}
